% =====================================================================
% Anhang D: Literatur
% =====================================================================

\chapter{Literatur}

\label{app:literatur}

\begin{thebibliography}{99}

\bibitem{aegis2026}
Chakraborty, A., \& Singh, R. (2026).
\newblock \foreign{Taming the Black Swan: A Momentum-Gated Hierarchical Optimisation Framework for Asymmetric Alpha Generation}.
\newblock arXiv:2604.09060v1 [cs.CE].
\newblock Birla Institute of Technology Mesra, Ranchi, India.

\bibitem{jegadeesh1993}
Jegadeesh, N., \& Titman, S. (1993).
\newblock \foreign{Returns to Buying Winners and Selling Losers: Implications for Stock Market Efficiency}.
\newblock \emph{Journal of Finance}, 48(1), 65--91.

\bibitem{sharpe1966}
Sharpe, W. F. (1966).
\newblock \foreign{Mutual Fund Performance}.
\newblock \emph{Journal of Business}, 39(1), 119--138.

\bibitem{sortino1994}
Sortino, F. A., \& Price, L. N. (1994).
\newblock \foreign{Performance Measurement in a Downside Risk Framework}.
\newblock \emph{Journal of Investing}, 3(3), 59--64.

\bibitem{markowitz1952}
Markowitz, H. (1952).
\newblock \foreign{Portfolio Selection}.
\newblock \emph{Journal of Finance}, 7(1), 77--91.

\bibitem{capm}
Sharpe, W. F. (1964).
\newblock \foreign{Capital Asset Prices: A Theory of Market Equilibrium under Conditions of Risk}.
\newblock \emph{Journal of Finance}, 19(3), 425--442.

\bibitem{famafrench1993}
Fama, E. F., \& French, K. R. (1993).
\newblock \foreign{Common Risk Factors in the Returns on Stocks and Bonds}.
\newblock \emph{Journal of Financial Economics}, 33(1), 3--56.

\bibitem{carhart1997}
Carhart, M. M. (1997).
\newblock \foreign{On Persistence in Mutual Fund Performance}.
\newblock \emph{Journal of Finance}, 52(1), 57--82.

\bibitem{asness2013}
Asness, C. S., Frazzini, A., Israel, R., \& Moskowitz, T. J. (2013).
\newblock \foreign{Trading Anomaly: A Buy-Side Perspective}.
\newblock AQR Capital Management working paper.

\bibitem{sornette2003}
Sornette, D. (2003).
\newblock \foreign{Why Stock Markets Crash: Critical Events in Complex Financial Systems}.
\newblock Princeton University Press.

\bibitem{taleb2010}
Taleb, N. N. (2010).
\newblock \foreign{The Black Swan: The Impact of the Highly Improbable}.
\newblock Random House.

\bibitem{opaque}
Taleb, N. N. (2018).
\newblock \foreign{Antifragile: Things That Gain from Disorder}.
\newblock Random House.

\bibitem{ecb2023}
European Central Bank (2023).
\newblock \foreign{Statistical Data Warehouse -- SDMX 2.1 REST API Documentation}.
\newblock \url{https://data-api.ecb.europa.eu/documentation}.

\bibitem{fredapi}
Federal Reserve Bank of St.\ Louis (2024).
\newblock \foreign{FRED API Documentation}.
\newblock \url{https://fred.stlouisfed.org/docs/api/}.

\bibitem{opentui}
Anomaly Cooperative (2025).
\newblock \foreign{OpenTUI -- Terminal UIs on a Native Zig Core}.
\newblock \url{https://opentui.com}.

\bibitem{react19}
Meta Open Source (2024).
\newblock \foreign{React 19 Documentation}.
\newblock \url{https://react.dev}.

\bibitem{tsc}
Microsoft Corporation (2024).
\newblock \foreign{TypeScript Handbook}.
\newblock \url{https://www.typescriptlang.org/docs/handbook/}.

\bibitem{bun}
Oven (2024).
\newblock \foreign{Bun -- A fast all-in-one JavaScript runtime}.
\newblock \url{https://bun.sh}.

\bibitem{sqlalchemy}
Bayer, M. (2024).
\newblock \foreign{SQLAlchemy 2.0 Documentation}.
\newblock \url{https://docs.sqlalchemy.org/en/20/}.

\bibitem{polars}
Vermeulen, R. (2024).
\newblock \foreign{Polars -- Lightning-fast DataFrame library}.
\newblock \url{https://pola.rs}.

\bibitem{prefect2}
Prefect Technologies (2024).
\newblock \foreign{Prefect 2.x Documentation}.
\newblock \url{https://docs.prefect.io}.

\bibitem{plotly}
Plotly Technologies (2024).
\newblock \foreign{Plotly Python Open Source Graphing Library}.
\newblock \url{https://plotly.com/python/}.

\bibitem{tenacity}
Kuchling, A. (2024).
\newblock \foreign{tenacity -- Retrying library for Python}.
\newblock \url{https://tenacity.readthedocs.io}.

\bibitem{structlog}
Werk, H. (2024).
\newblock \foreign{structlog -- Structured Logging for Python}.
\newblock \url{https://www.structlog.org}.

\bibitem{pyoett}
Pydantic (2024).
\newblock \foreign{pydantic-settings -- Settings management using Pydantic}.
\newblock \url{https://docs.pydantic.dev/latest/concepts/pydantic_settings/}.

\bibitem{alembic}
Bayer, M. (2024).
\newblock \foreign{Alembic -- Database migrations for SQLAlchemy}.
\newblock \url{https://alembic.sqlalchemy.org}.

\bibitem{docker}
Docker Inc. (2024).
\newblock \foreign{Docker Documentation}.
\newblock \url{https://docs.docker.com}.

\bibitem{postgresql}
PostgreSQL Global Development Group (2024).
\newblock \foreign{PostgreSQL 16 Documentation}.
\newblock \url{https://www.postgresql.org/docs/16/}.

\bibitem{ruff}
Charlier, C. (2024).
\newblock \foreign{Ruff -- An extremely fast Python linter and code formatter}.
\newblock \url{https://docs.astral.sh/ruff/}.

\bibitem{mypy}
Lehtosalo, J. (2024).
\newblock \foreign{mypy -- Optional static typing for Python}.
\newblock \url{https://mypy.readthedocs.io}.

\bibitem{pytest}
Krekel, H. (2024).
\newblock \foreign{pytest -- A mature full-featured Python testing tool}.
\newblock \url{https://docs.pytest.org}.

\bibitem{yfinance}
Aroussi, R. (2024).
\newblock \foreign{yfinance -- Download market data from Yahoo! Finance API}.
\newblock \url{https://github.com/ranaroussi/yfinance}.

\bibitem{httpx}
Encode OSS (2024).
\newblock \foreign{httpx -- A next-generation HTTP client for Python}.
\newblock \url{https://www.python-httpx.org}.

\bibitem{nodepg}
brianc (2024).
\newblock \foreign{node-postgres -- PostgreSQL client for Node.js}.
\newblock \url{https://node-postgres.com}.

\end{thebibliography}
